05 - PubliliaFitness - Estimating lifetime fecundity and fitness

### 2023-08-26 scripts/Publilia-05-fitness.Rmd
Moved Zink fitness analysis to it's own script + saved survorship model fits from script 03 to use in 05 + other minor edits to script 05 to run without error

```{r}
surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
```

@@

# v6: (survivorship ~ ant_treatment * I(desL^2)) * proportion of time on eggs
est_fitness_hatch_fit_v6 <- 
  ci_for_fitness(data_in=est_fitness_prep, model=des_hatch.desL.ant_treatment.quad.fits$mai.qb) %>%
  mutate(est_hatch_fit_v6 = fit) %>%
  select(-(fit:conf_lwr))
est_fitness_Esurv_fit_v6 <- 
  ci_for_fitness(data_in=est_fitness_hatch_fit_v6, model=des_Esurv.desL.ant_treatment.quad.fits$mai.qb) %>%
  mutate(est_Esurv_fit_v6 = fit) %>%
  select(-(fit:conf_lwr))

@@

## Comparing to Zink 2003 method

### 3 Zink 2003 model:
Lifetime fitness (number of eggs that hatched):
w(t_i) = sum(from i=1, to i=N, P_i*g(t_i))
P = number of eggs invested in a clutch (all the eggs go to the initiator?)
t_i = guarding duration in clutch i
N = lifetime number of clutches
g(t) = relationship between guarding duration and hatching success
 (assume g(t) equivalent across all clutches 1 to N)

* I think the main reason Zink found equivalent fitness is that he attributed all the eggs in a clutch to each primary female. Thus an early deserter is given all the eggs from a clutch, even if she leaves within a few days and another female arrives and lays additional eggs. The final nail in the coffin will be to do the exact same "zink" estimates but this time only attributing the egg to each female proportional to the time she spent on the clutch relative to other females.
```{r}
surv_reg_data_zink <- focalMb4h_sc2h %>%
  filter(!is.na(initiation_date), !is.na(guard_duration), !ants_removed) %>%
  filter(mom_at_init) %>% # primary females
  group_by(location) %>%
    summarize(max_primary_dur = max(guard_duration, na.rm=T),
              females_removed = first(females_removed),
              initiation_date = first(initiation_date)) %>%
  ungroup() %>%
  left_join(top5eggs_summary) %>%
  select(location, max_primary_dur,
         females_removed, initiation_date, med_t5eggs) %>%
  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
            by=c("location"="NOr_rev_loc")) %>%
  select(location, initiation_date, hatch_date, 
         max_primary_dur, med_t5eggs, n_hatched, n_survived,
         females_removed)

ggplot(data=surv_reg_data_zink, 
       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
  geom_point() +
  geom_smooth(method=lm)

ggplot(data=filter(surv_reg_data_zink, initiation_date<=as_date("2019-06-10")), 
       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
  geom_point() +
  geom_smooth(method=lm)

ggplot(data=filter(surv_reg_data_zink, initiation_date<=as_date("2019-06-10"), !females_removed), 
       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
  geom_point() +
  geom_smooth(method=lm)

zink_hatch.m <- surv_reg_data_zink %>%
  filter(initiation_date<=as_date("2019-06-10"), !is.na(n_hatched/med_t5eggs)) %>%
lm(n_hatched/med_t5eggs ~ max_primary_dur, data=.)

summary(zink_hatch.m) # use this for predicting hatching success

zink_hatch.m.norem <- surv_reg_data_zink %>%
  filter(initiation_date<=as_date("2019-06-10"), !is.na(n_hatched/med_t5eggs), !females_removed) %>%
lm(n_hatched/med_t5eggs ~ max_primary_dur, data=.)

summary(zink_hatch.m.norem)

est_fitness_clutch_zink <- focalMb4h_sc2h %>%
  filter(!is.na(initiation_date), !ants_removed) %>%
  group_by(location) %>%
    mutate(max_primary_dur = max(mom_at_init*guard_duration, na.rm=T)) %>% # non-primary females are not counted
  ungroup() %>%
  left_join(top5eggs_summary) %>%
  left_join(clutch_momDays_b4h) %>%
  select(Female_ID, location, guard_duration, max_primary_dur, desert_rel2h=est_rel2h, focalMb4h_sc2h, mDb4h_sc2h,
         females_removed, initiation_date, med_t5eggs, 
         mom_at_init, clutch_visited_order, clutch_initiated_order) %>%
  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
            by=c("location"="NOr_rev_loc")) %>%
  select(Female_ID, location, initiation_date, hatch_date, 
         guard_duration, max_primary_dur, desert_rel2h, focalMb4h_sc2h, mDb4h_sc2h,
         med_t5eggs, n_hatched, n_survived, females_removed,
         mom_at_init, clutch_visited_order, clutch_initiated_order) %>%
  mutate(propD_b4h = focalMb4h_sc2h/mDb4h_sc2h,
         est_eggs_clutch = med_t5eggs*propD_b4h,
         zink_est_hatch_clutch_v1 = med_t5eggs*(coef(zink_hatch.m)[[1]]+guard_duration*coef(zink_hatch.m)[[2]]),
         zink_est_hatch_clutch_v2 = est_eggs_clutch*(coef(zink_hatch.m)[[1]]+guard_duration*coef(zink_hatch.m)[[2]])) %>%
  group_by(Female_ID) %>%
    mutate(zink_est_hatch_life_v1 = sum(zink_est_hatch_clutch_v1, na.rm=T),
           zink_est_hatch_life_v2 = sum(zink_est_hatch_clutch_v2, na.rm=T)) %>%
  ungroup()

est_fitness_life_strats_Zink <- est_fitness_clutch_zink %>%
  group_by(Female_ID) %>%
  # clutch visited order == 0 means she visited before initiation, so it shouldn't count
  mutate(started_by =
           ifelse(any(clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order==1),
                  "initiating",
                  ifelse(any(clutch_visited_order==1&is.na(clutch_initiated_order)|
                             clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order!=1),
                         "visiting", "other")),
         n_clutches_with_eggs_iv = sum(!is.na(clutch_visited_order)&(clutch_visited_order>0), na.rm=T)) %>%
  ungroup() %>%
  filter(clutch_visited_order==1) %>%
  # mutate(desert_cat = ifelse(started_by=="initiating",
  #                                ifelse(desert_rel2h <= -16, "desert",
  #                                       ifelse(desert_rel2h > -16 & desert_rel2h <= 4, "eggs", 
  #                                              ifelse(desert_rel2h >= 4,"nymphs",
  #                                                     NA))),
  #                                ifelse(started_by=="visiting", "visit", 
  #                                       NA)),
  mutate(desert_cat = ifelse(started_by=="initiating",
                                 ifelse(guard_duration <= 10, "desert",
                                        ifelse(guard_duration > 10 & desert_rel2h <= 4, "eggs", 
                                               ifelse(guard_duration >= 4,"nymphs",
                                                      NA))),
                                 ifelse(started_by=="visiting", "visit", 
                                        NA)),
         zink_dur_cat = ifelse(started_by=="initiating",
                               ifelse(guard_duration<12, "desert",
                                      ifelse(guard_duration>=12, "stay", NA)),
                               ifelse(started_by=="visiting", "visit", 
                                        NA))) %>%
  distinct(Female_ID, females_removed,
           guard_duration, max_primary_dur,
           started_by, desert_cat, zink_dur_cat,
           zink_est_hatch_clutch_v1, zink_est_hatch_clutch_v2,
           zink_est_hatch_life_v1, zink_est_hatch_life_v2,
           n_clutches_with_eggs_iv)

# v1: Zink 2003 attributes all egg in a clutch to the primary female, even if they desert early and a visitor laid additional eggs
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v1, fill=zink_dur_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  ggtitle("v1: all eggs in clutch to primary female")

# v2: all calculations the same, but give eggs to females in proportion to the time they spent at clutch relative to other females
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v2, fill=zink_dur_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  ggtitle("v2: eggs to female by proportion of time guarding")

# same but separating females that laid one vs. multiple clutches
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v1, fill=zink_dur_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
  ggtitle("v1: all eggs in clutch to primary female")

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v2, fill=zink_dur_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
  ggtitle("v2: eggs to female by proportion of time guarding")

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v1, fill=desert_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  ggtitle("v1: all eggs in clutch to primary female")

# same but using desert_cat instead of Zink 2003 cats
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v1, fill=desert_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
  ggtitle("v1: all eggs in clutch to primary female")

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v2, fill=desert_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  ggtitle("v2: eggs to female by proportion of time guarding")

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v2, fill=desert_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
  ggtitle("v2: eggs to female by proportion of time guarding")

@@

## First clutch vs. future fecundity and fitness
Fecundity
```{r}
fitness_life_strats_data <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs"),
         desert_cat_ants = ifelse(ants_removed, 
                                 paste(desert_cat,"ants removed"),paste(desert_cat,"control")),
         desert_cat_ants = factor(desert_cat_ants,
          levels=c("visit control", "desert control", "eggs control","nymphs control",
                   "visit ants removed", "desert ants removed", "eggs ants removed","nymphs ants removed")))

@@

fitness_first_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_clutch, group=desert_cat, 
                    itero=F, multcompLetters=fitness_first_stats_eggs_v6$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("First-clutch fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_future, group=desert_cat, 
                    itero=F, multcompLetters=fitness_future_stats_eggs_v6$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("Future fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_eggs_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_eggs.itero$multcompLetters,
                    letterSize=letterSize, ymax=160)$itero +
  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_life_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_life_stats_eggs_v6$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none")

@@

fitness_future_stats_hatched_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_hatched_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_hatched.itero$multcompLetters,
                    letterSize=letterSize, ymax=75)$itero +
  ylab("Multi-clutch future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_survived_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_survived_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_survived.itero$multcompLetters,
                    letterSize=letterSize, ymax=22)$itero +
  ylab("Multi-clutch future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

@@

fitness_future_stats_eggs_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_eggs_future, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_eggs.itero.DEN$multcompLetters,
                    letterSize=letterSize, ymax=160)$itero +
  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_hatched_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_hatched_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_hatched.itero.DEN$multcompLetters,
                    letterSize=letterSize, ymax=75)$itero +
  ylab("Multi-clutch future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_survived_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_survived_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_survived.itero.DEN$multcompLetters,
                    letterSize=letterSize, ymax=22)$itero +
  ylab("Multi-clutch future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

@@

fitness_future_stats_hatched_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_future_v6, group=desert_cat, 
                    multcompLetters=fitness_future_stats_hatched$multcompLetters,
                    letterSize=letterSize, ymax=75) +
  ylab("Future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_survived_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_future_v6, group=desert_cat, 
                    multcompLetters=fitness_future_stats_survived$multcompLetters,
                    letterSize=letterSize, ymax=22) +
  ylab("Future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

@@

fitness_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_eggs_v6$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_hatched_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_hatched_v6$multcompLetters,
                    letterSize=letterSize, ymax=100) +
  ylab("Lifetime fitness\n(eggs hatched)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_survived_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_survived_v6$multcompLetters,
                    letterSize=letterSize, ymax=30) +
  ylab("Lifetime fitness\n(nymphs survived)") + 
  theme(legend.position=c(0.3,0.9))

@@

ggsave("fitness_stats.violin.final.png",
       fitness_stats.v6.p.final,
       device = "png",
       width = 120, height = 200, units = "mm", dpi = "print")
```

@@

fitness_stats_eggs_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_eggs_v1$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_hatched_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_hatched_v1$multcompLetters,
                    letterSize=letterSize, ymax=100) +
  ylab("Lifetime fitness\n(eggs hatched)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_survived_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_survived_v1$multcompLetters,
                    letterSize=letterSize, ymax=30) +
  ylab("Lifetime fitness\n(nymphs survived)") + 
  theme(legend.position=c(0.3,0.9))

@@

ggsave("fitness_stats.supp_v1.violin.final.png",
       fitness_stats.v1.p.final,
       device = "png",
       width = 120, height = 200, units = "mm", dpi = "print")
```

@@

fitness_stats_eggs.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_eggs.semel$multcompLetters,
                    letterSize=letterSize, ymax=160)$semel +
  ylab("Single-clutch female\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_eggs.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_eggs.itero$multcompLetters,
                    letterSize=letterSize, ymax=160)$itero +
  ylab("Multi-clutch female\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_hatched.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_hatched.semel$multcompLetters,
                    letterSize=letterSize, ymax=100)$semel +
  ylab("Single-clutch female\nfitness (eggs hatched)") + 
    theme(legend.position=c(0.3,0.8), axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_hatched.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_hatched.itero$multcompLetters,
                    letterSize=letterSize, ymax=100)$itero +
  ylab("Multi-clutch female\nfitness (eggs hatched)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_survived.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_survived.semel$multcompLetters,
                    letterSize=letterSize, ymax=30)$semel +
  ylab("Single-clutch female\nfitness (nymphs survived)") + 
    theme(legend.position="none")

@@

fitness_stats_survived.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_survived.itero$multcompLetters,
                    letterSize=letterSize, ymax=30)$itero +
  ylab("Multi-clutch female\nfitness (nymphs survived)") + 
    theme(legend.position="none")

@@

ggsave("fitness_stats.violin.parity.final.png",
       fitness_stats.parity.p.final,
       device = "png",
       width = 200, height = 200, units = "mm", dpi = "print")
```

## Comparing to Zink 2003 fitness measures
Lifetime fitness (number of eggs that hatched):
w(t_i) = sum(from i=1, to i=N, P_i*g(t_i))
P = number of eggs invested in a clutch (all the eggs go to the initiator?)
t_i = guarding duration in clutch i
N = lifetime number of clutches
g(t) = relationship between guarding duration and hatching success
 (assume g(t) equivalent across all clutches 1 to N)

>>>>

```{r}
surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
surv_model_fits <- read_rds(here("saved_rds/surv_model_fits.rds"))
```

@@

# v6: (survivorship ~ ant_treatment * I(desL^2)) * proportion of time on eggs
est_fitness_hatch_fit_v6 <- 
  ci_for_fitness(data_in=est_fitness_prep, model=surv_model_fits$hatch$mai.qb) %>%
  mutate(est_hatch_fit_v6 = fit) %>%
  select(-(fit:conf_lwr))
est_fitness_Esurv_fit_v6 <- 
  ci_for_fitness(data_in=est_fitness_hatch_fit_v6, model=surv_model_fits$Esurv$mai.qb) %>%
  mutate(est_Esurv_fit_v6 = fit) %>%
  select(-(fit:conf_lwr))

@@

@@

## First clutch vs. future fecundity and fitness

```{r}
letterSize <- 3
```

Fecundity
```{r}
fitness_life_strats_data <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs"),
         desert_cat_ants = ifelse(ants_removed, 
                                 paste(desert_cat,"ants removed"),paste(desert_cat,"control")),
         desert_cat_ants = factor(desert_cat_ants,
          levels=c("visit control", "desert control", "eggs control","nymphs control",
                   "visit ants removed", "desert ants removed", "eggs ants removed","nymphs ants removed")))

@@

fitness_first_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_clutch, group=desert_cat, 
                    itero=F, multcompLetters=fitness_first_stats_eggs_v6$multcompLetters,ymax=160) +
  ylab("First-clutch fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_future, group=desert_cat, 
                    itero=F, multcompLetters=fitness_future_stats_eggs_v6$multcompLetters,
                    ymax=160) +
  ylab("Future fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_eggs_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_eggs.itero$multcompLetters,
                    ymax=160)$itero +
  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_life_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_life_stats_eggs_v6$multcompLetters,
                    ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none")

@@

fitness_future_stats_hatched_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_hatched_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_hatched.itero$multcompLetters,
                    ymax=75)$itero +
  ylab("Multi-clutch future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_survived_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_survived_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_survived.itero$multcompLetters,
                    ymax=22)$itero +
  ylab("Multi-clutch future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

@@

fitness_future_stats_eggs_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_eggs_future, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_eggs.itero.DEN$multcompLetters,
                    ymax=160)$itero +
  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_hatched_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_hatched_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_hatched.itero.DEN$multcompLetters,
                    ymax=75)$itero +
  ylab("Multi-clutch future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_survived_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_survived_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_survived.itero.DEN$multcompLetters,
                    ymax=22)$itero +
  ylab("Multi-clutch future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

@@

fitness_future_stats_hatched_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_future_v6, group=desert_cat, 
                    multcompLetters=fitness_future_stats_hatched$multcompLetters,
                    ymax=75) +
  ylab("Future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_future_stats_survived_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_future_v6, group=desert_cat, 
                    multcompLetters=fitness_future_stats_survived$multcompLetters,
                    ymax=22) +
  ylab("Future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

@@

fitness_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_eggs_v6$multcompLetters,
                    ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_hatched_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_hatched_v6$multcompLetters,
                    ymax=100) +
  ylab("Lifetime fitness\n(eggs hatched)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_survived_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_survived_v6$multcompLetters,
                    ymax=30) +
  ylab("Lifetime fitness\n(nymphs survived)") + 
  theme(legend.position=c(0.3,0.9))

@@

ggsave(here("prelim_figs/Publilia-05-fitness/fitness_stats.violin.final.png"),
       fitness_stats.v6.p.final,
       device = "png",
       width = 120, height = 200, units = "mm", dpi = "print")
```

@@

fitness_stats_eggs_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_eggs_v1$multcompLetters,
                    ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_hatched_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_hatched_v1$multcompLetters,
                    ymax=100) +
  ylab("Lifetime fitness\n(eggs hatched)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_survived_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_survived_v1$multcompLetters,
                    ymax=30) +
  ylab("Lifetime fitness\n(nymphs survived)") + 
  theme(legend.position=c(0.3,0.9))

@@

ggsave(here("prelim_figs/Publilia-05-fitness/fitness_stats.supp_v1.violin.final.png"),
       fitness_stats.v1.p.final,
       device = "png",
       width = 120, height = 200, units = "mm", dpi = "print")
```

@@

fitness_stats_eggs.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_eggs.semel$multcompLetters,
                    ymax=160)$semel +
  ylab("Single-clutch female\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_eggs.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_eggs.itero$multcompLetters,
                    ymax=160)$itero +
  ylab("Multi-clutch female\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_hatched.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_hatched.semel$multcompLetters,
                    ymax=100)$semel +
  ylab("Single-clutch female\nfitness (eggs hatched)") + 
    theme(legend.position=c(0.3,0.8), axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_hatched.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_hatched.itero$multcompLetters,
                    ymax=100)$itero +
  ylab("Multi-clutch female\nfitness (eggs hatched)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

@@

fitness_stats_survived.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_survived.semel$multcompLetters,
                    ymax=30)$semel +
  ylab("Single-clutch female\nfitness (nymphs survived)") + 
    theme(legend.position="none")

@@

fitness_stats_survived.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_survived.itero$multcompLetters,
                    ymax=30)$itero +
  ylab("Multi-clutch female\nfitness (nymphs survived)") + 
    theme(legend.position="none")

@@

ggsave(here("prelim_figs/Publilia-05-fitness/fitness_stats.violin.parity.final.png"),
       fitness_stats.parity.p.final,
       device = "png",
       width = 200, height = 200, units = "mm", dpi = "print")
```
